Making Sense of Tweets: Student research projects in data science

### 2019-09-17 Rmd/abstract.Rmd
rewrote abstract in response to BH comments

Social media platforms have altered the way that we communicate. The tremendous volumes of streaming data that are available through platforms like Twitter and Facebook enable the investigation of new data science research questions. In many cases, these research questions may serve as engaging and scientifically meaningful studies for those who are new to data science research. 
In seeking to explore social media data science as a pedagogical tool, we guided two undergraduate researchers during the 2015-2016 academic year while they completed mentored research projects.

>>>>

Social media platforms have altered communication methods. The tremendous volumes of streaming data that are available through platforms like Twitter and Facebook enable the investigation of new data science research questions. In many cases, these research questions may motivate engaging, accessible, and scientifically meaningful studies for data science research students.
In seeking to explore social media data science as a pedagogical tool, we developed a teaching and mentoring framework to guide undergraduate researchers through individualized research projects. We demonstrated our approach by guiding two undergraduate researchers while they completed research projects. Our framework involves research question formulation, data acquisition, data analysis and visualization, and presentation of results. Our two student projects, which serve as case studies for our framework, completed all components of the invididualized research projects. We found that research skills, self-confidence in research ability, and professional interest in data science increased for both students.
